Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Background.tex
adding tildas

If \reqFn{} is an input to the memory subsystem, and the set \Response{} is the
corresponding output, then the memory subsystem is said to be \textbf{store atomic} if it
obeys Theorem \fullref{storeAtomicity} defined as follows. We use the word
``response'' to denote an element in the set \Response{}.
%
\begin{defn} (Responses have unique labels.)
\small
\begin{multline*}
\textit{uniqRespLabels} := \forall (r_1, r_2 \in \Response). \;
r_1.\labelR = r_2.\labelR @-> \\ r_1.\timeR = r_2.\timeR \wedge
r_1.\dataR = r_2.\dataR
\end{multline*}
\label{uniqRespLabels}
\end{defn}

>>>>

If \reqFn{} is an input to the memory subsystem, and the set \Response{} is the
corresponding output, then the memory subsystem is said to be \textbf{store atomic} if it
obeys Theorem~\fullref{storeAtomicity} defined as follows. We use the word
``response'' to denote an element in the set \Response{}.
%
\begin{defn} (Responses have unique labels.)
\small
\begin{multline*}
\textit{uniqRespLabels} := \forall (r_1, r_2 \in \Response). \;
r_1.\labelR = r_2.\labelR @-> \\ r_1.\timeR = r_2.\timeR \wedge
r_1.\dataR = r_2.\dataR
\end{multline*}
\label{uniqRespLabels}
\end{defn}
